CSD, Disjoint components and trayectory detection

### 2019-11-08 ArticuloCSDyCM/Paper03.tex
Estriado 1004AP es el bueno

>>>>

 Larger scale recordings (macroscopic
structures) may gain something of this analysis, but we shall focus
our result to the neurons scale ( distances of the order of \mum{10}).

The stratial tissue is an example of where this analysis cannot be used.
The limitations of this analysis are that it works  in
ordered, stratified neuronal tissue, and highly homogeneous tissue
without clear structures makes the distintion of both the CSD
disconnected sets unfeasible.
